---
title: "COVIDCNS Cognitive Analysis Correlations"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "scripts/functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )
  
# Check variable names in dataframe
dat %>%
  colnames()

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

## Correlations


Correlation Matrix and Plot
```{r Correlation matrix of all variables}
corr_dat <- data_joined %>%
  select(
    `Age` = "dem.dob_age",
    `Sex` = "dem.sex_at_birth_numeric",
    `Memory Concerns` = "dem.concerned_memory_numeric",
    `Education` = "dem.highest_education_numeric",
    `COVID19 Severity` = "ncrf1_vital.admission_severity_worst_covid19_numeric",
    `Clinical Frailty` = "ncrf1_comorbid.clinical_frailty_scale_numeric",
    `GAD7` = "gad7.sum_score",
    `PHQ9` = "phq9.sum_score",
    `PCL5` = "pcl5.sum_score",
    `CFS` = "cfs.sum_score",
    `Corticosteroids` = "ncrf2_med.corticosteroid_numeric"
 ) 

corr_out <- psych::mixedCor(data = corr_dat,
                            c = c(1,3:11),
                            d = c(2),
                            use = "pairwise.complete.obs")

corr_out_rmat <- corr_out$rho


# Write file path to save plot
png(file = "analysis/correlations/corr_matrix.png")
# Create correlation matrix with hierarchical clustering
corr_matrix_plot <- corrplot::corrplot(corr_out_rmat, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 1,
         cl.cex = 1,
         order = "original",
         tl.col = "black",
         cl.align.text = "c",
         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         number.font = 0.5,
         number.cex = 0.5, # size of co-efficients
         sig.level = 0.01, # Choose significant level
         insig = "blank", # Nonsignificant correlations have no colour,
         bg = "white"
         )
# Save plot
dev.off()

```
