---
title: "COVIDCNS Cognitive Analysis ETL Script"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in raw data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data_raw/covidcns_greta.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

Select variables relevant to analysis only as listed in OSF plus others required
```{r Select analysis variables}
dat %>%
  select(
    ID,
    # sample level groupings
    case_control_vaccine,
    diagnostic_group,
    # baseline demographics
    dem.dob_age,
    dem.sex_at_birth,
    dem.highest_education,
    dem.concerned_memory,
    # mh questionnaires
    gad7.sum_score,
    phq9.sum_score,
    pcl5.sum_score,
    # ncrf data
    ncrf1_vital.admission_severity_worst_covid19,
    ncrf1_comorbid.clinical_frailty_scale,
    ncrf1_admission_windowed,
    ncrf2_med.corticosteroid,
    # cognitron demographics
    age1,
    age2,
    decade,
    sex,
    language,
    education,
    DEVICE,
    # cognitron task scores
    rs_prospectiveMemoryWords_1_immediate,
    rs_spatialSpan,
    rs_manipulations2D,
    rs_verbalAnalogies,
    rs_prospectiveMemoryWords_1_delayed,
    rs_TOL,
    rs_targetDetection,
    # cognitron task RTs
    rs_prospectiveMemoryWords_1_immediate_RT,
    rs_spatialSpan_RT,
    rs_manipulations2D_RT,
    rs_verbalAnalogies_RT,
    rs_prospectiveMemoryWords_1_delayed_RT,
    rs_TOL_RT,
    rs_targetDetection_RT,
    # cognitron task DfE scores
    rs_manipulations2D_dfe,
    rs_TOL_dfe,
    rs_prospectiveMemoryWords_1_delayed_dfe,
    rs_prospectiveMemoryWords_1_immediate_dfe,
    rs_spatialSpan_dfe,
    rs_targetDetection_dfe,
    rs_verbalAnalogies_dfe,
    # cognitron task DfE RTs
    rs_manipulations2D_RT_dfe,
    rs_TOL_RT_dfe,
    rs_prospectiveMemoryWords_1_delayed_RT_dfe,
    rs_prospectiveMemoryWords_1_immediate_RT_dfe,
    rs_spatialSpan_RT_dfe,
    rs_targetDetection_RT_dfe,
    rs_verbalAnalogies_RT_dfe,
    # cognitron composite scores
    Composite_global,
    Composite_acc,
    Composite_rt
  )

```



Recode Non-answer values to NA
-555 'Not applicable' response from participant
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say
`NA` Were not shown the question (genuinely missing value)
When we code someone as being 'not applicable' by deduction, we use `NA_real_`
```{r Recode NA values}
dat <- dat %>%
  mutate(across(where(is.numeric),
                ~case_when(
                  . == -555 ~ NA_real_,
                  . == -777 ~ NA_real_,
                  . == -888 ~ NA_real_,
                  . == -999 ~ NA_real_,
                  TRUE ~ .)
                )
         )

non_ans_vals <- c(
  "Not applicable",
  "Seen but not answered",
  "Don't know",
  "Prefer not to answer",
  "Prefer not to say"
)

dat %>% mutate_all(~ na_if(., . == "Seen but not answered"))

```

Add windowed inpatient admission variable
```{r Window inpatient admission}
dat <- dat %>%
  mutate(
    ncrf1_admission_windowed =
      case_when(ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2020-03-01") & ncrf1_admission.date_of_inpatient_admission.txt <= as.POSIXct("2020-09-01")  ~ "March 2020 to August 2020",
                
                ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2020-09-01") & ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2021-03-01")  ~ "September 2020 to February 2021",
                
                ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2021-03-01") & ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2021-09-01")  ~ "March 2021 to August 2021",
                
                ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2021-09-01") & ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2022-03-01")  ~ "September 2021 to February 2022",
                is.na(ncrf1_admission.date_of_inpatient_admission.txt) ~ "Missing",
                ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2020-03-01") | ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2022-03-01")  ~ "Other"
                )
    )
```

Simplify COVID19 severity
```{r Simplify severity}
dat <- dat %>%
  mutate(across(ncrf1_vital.admission_severity_worst_covid19,
                ~case_when(
        . == "Uninfected (No viral RNA detected)" ~ "Uninfected",
        . == "Asymptomatic (Viral RNA detected)" |
          . == "Symptomatic (Independent)"	|
          . == "Symptomatic (Assistance needed)" ~ "Ambulatory mild disease",
        . == "Hospitalised (No oxygen therapy)" |
          . == "Hospitalised (Oxygen by mask or nasal prongs)" ~ "Hospitalised: moderate disease",
        . == "Hospitalised (Oxygen by NIV or high flow)" |
          . == "Intubation and mechanical ventilation (pO2/FiO2 >= 150 or SpO2/FiO2 >= 200)" |
          . == "Mechanical ventilation (pO2/FiO2 <150 or SpO2/FiO2 <200 or vasopressors)" |
          . == "Mechanical ventilation (pO2/FiO2 <150 and vasopressors, dialysis or ECMO)" ~ "Hospitalised: severe disease",
        is.na(.) ~ NA_character_)
        )
    )
```

Save data
```{r Write to .rds file}
dat %>%
  saveRDS(
    file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
    )
```