---
title: "COVIDCNS Cognitive Analysis Data Visualisation"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "scripts/functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )
  
# Check variable names in dataframe
dat %>%
  colnames()

# Inspect dimensions of dataframe 
dat %>%
  dim()
```



# Plots


# Plots of Composite Scores


Violin plot cognitron global by diagnostic group
```{r violin plot global cognitron}
pl1 <- ggplot(
  data = subset(dat,!is.na(diagnostic_group) & !is.na(Composite_global)), # remove NAs from plotting vars
  aes(x = diagnostic_group, y = Composite_global, fill = diagnostic_group) # plot and fill by diag group
  )

# violin plot
pl1 <- pl1 + geom_violin(trim = F)

# add summary stat line
pl1 <- pl1 + stat_summary(fun.data=mean_sdl, # can use median_hilow instead
                          geom="pointrange",
                          color="cyan")

pl1 <- pl1 + xlab("Diagnostic Group")

pl1 <- pl1 + ylab("Cognitron Global Score (DfE)")

pl1 <- pl1 + labs(fill = "Diagnostic Group")

pl1 <- pl1 + scale_fill_brewer(palette = "Accent")

pl1 <- pl1 + theme_bw()

pl1 <- pl1 + 
  ggtitle("Cognitron Global Score (DfE) by Diagnostic Group in the COVIDCNS Study") + 
  theme(plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl1

ggsave("plots/bydiagnosis/cognitron_global_bydiag_violplot.png")
```


Violin plot cognitron accuracy by diagnostic group
```{r violin plot acc cognitron}
pl2 <- ggplot(data = subset(dat,
                            !is.na(diagnostic_group) &
                              !is.na(Composite_acc)),
              aes(x = diagnostic_group,
                  y = Composite_acc,
                  fill = diagnostic_group))

pl2 <- pl2 + geom_violin(trim = F)

pl2 <- pl2 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl2 <- pl2 + xlab("Diagnostic Group")

pl2 <- pl2 + ylab("Cognitron Accuracy Score (DfE)")

pl2 <- pl2 + labs(fill = "Diagnostic Group")

pl2 <- pl2 + scale_fill_brewer(palette = "Accent")

pl2 <- pl2 + theme_bw()

pl2 <- pl2 +
  ggtitle("Cognitron Accuracy Score (DfE) by Diagnostic Group in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl2

ggsave("plots/bydiagnosis/cognitron_acc_bydiag_violplot.png")
```

Violin plot cognitron RT by diagnostic group
```{r violin plot rt cognitron}
pl3 <- ggplot(data = subset(dat,
                            !is.na(diagnostic_group) &
                              !is.na(Composite_rt)),
              aes(x = diagnostic_group,
                  y = Composite_rt,
                  fill = diagnostic_group))

pl3 <- pl3 + geom_violin(trim = F)

pl3 <- pl3 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl3 <- pl3 + xlab("Diagnostic Group")

pl3 <- pl3 + ylab("Cognitron RT Score (DfE)")

pl3 <- pl3 + labs(fill = "Diagnostic Group")

pl3 <- pl3 + scale_fill_brewer(palette = "Accent")

pl3 <- pl3 + theme_bw()

pl3 <- pl3 + 
  ggtitle("Cognitron RT Score (DfE) by Diagnostic Group in the COVIDCNS Study") + 
  theme(plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl3

ggsave("plots/bydiagnosis/cognitron_rt_bydiag_violplot.png")
```


# Plots by Task


Create vectors of cognitron task colnames
```{r Vectors cognitron tasks}
cogni_cols_demographics <- c(
  "age1",
  "age2",
  "decade",
  "sex",
  "language",
  "education",
  "DEVICE"
)

cogni_cols_tasks <- c(
  "rs_prospectiveMemoryWords_1_immediate",
  "rs_spatialSpan",
  "rs_manipulations2D",
  "rs_verbalAnalogies",
  "rs_prospectiveMemoryWords_1_delayed",
  "rs_TOL",
  "rs_targetDetection"
)

cogni_cols_tasks_RT <- c(
  "rs_prospectiveMemoryWords_1_immediate_RT",
  "rs_spatialSpan_RT",
  "rs_manipulations2D_RT",
  "rs_verbalAnalogies_RT",
  "rs_prospectiveMemoryWords_1_delayed_RT",
  "rs_TOL_RT",
  "rs_targetDetection_RT"
)

cogni_cols_dfe_tasks <- c(
  "rs_manipulations2D_dfe",
  "rs_TOL_dfe",
  "rs_prospectiveMemoryWords_1_delayed_dfe",
  "rs_prospectiveMemoryWords_1_immediate_dfe",
  "rs_spatialSpan_dfe",
  "rs_targetDetection_dfe",
  "rs_verbalAnalogies_dfe"
)

cogni_cols_dfe_tasks_RT <- c(
  "rs_manipulations2D_RT_dfe",
  "rs_TOL_RT_dfe",
  "rs_prospectiveMemoryWords_1_delayed_RT_dfe",
  "rs_prospectiveMemoryWords_1_immediate_RT_dfe",
  "rs_spatialSpan_RT_dfe",
  "rs_targetDetection_RT_dfe",
  "rs_verbalAnalogies_RT_dfe"
)

cogni_tasks_dat <- dat %>%
  select(
    all_of(
      cogni_cols_dfe_tasks
    )
  )

cogni_RT_dat <- dat %>%
  select(
    all_of(
      cogni_cols_dfe_tasks_RT
    )
  )
```

Subset tasks and RTs by case and control for plotting
```{r Subset tasks RTs case control}
cogni_tasks_case_dat <- dat %>%
  filter(case_control_vaccine == "Case: COVID-19 positive (i.e. neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks
    )
  )

cogni_tasks_control_dat <- dat %>%
  filter(case_control_vaccine == "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks
    )
  )

cogni_RT_case_dat <- dat %>%
  filter(case_control_vaccine == "Case: COVID-19 positive (i.e. neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks_RT
    )
  )

cogni_RT_control_dat <- dat %>%
  filter(case_control_vaccine == "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks_RT
    )
  )
```


Transform cognitron tasks wide to long to plot by task
```{r Transform wide long}
cogni_tasks_case_dat <- cogni_tasks_case_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_dfe" = "2D Manipulations",
                              "rs_TOL_dfe" = "TOL",
                              "rs_prospectiveMemoryWords_1_delayed_dfe" = "Word Memory Delayed",
                              "rs_prospectiveMemoryWords_1_immediate_dfe" = "Word Memory Immediate",
                              "rs_spatialSpan_dfe" = "Spatial Span",
                              "rs_targetDetection_dfe" = "Target Detection",
                              "rs_verbalAnalogies_dfe" = "Verbal Analogies")
                              
         )

cogni_tasks_control_dat <- cogni_tasks_control_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_dfe" = "2D Manipulations",
                              "rs_TOL_dfe" = "TOL",
                              "rs_prospectiveMemoryWords_1_delayed_dfe" = "Word Memory Delayed",
                              "rs_prospectiveMemoryWords_1_immediate_dfe" = "Word Memory Immediate",
                              "rs_spatialSpan_dfe" = "Spatial Span",
                              "rs_targetDetection_dfe" = "Target Detection",
                              "rs_verbalAnalogies_dfe" = "Verbal Analogies")
                              
         )

cogni_RT_case_dat <- cogni_RT_case_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks_RT),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_RT_dfe" = "2D Manipulations RT",
                              "rs_TOL_RT_dfe" = "TOL RT",
                              "rs_prospectiveMemoryWords_1_delayed_RT_dfe" = "Word Memory Delayed RT",
                              "rs_prospectiveMemoryWords_1_immediate_RT_dfe" = "Word Memory Immediate RT",
                              "rs_spatialSpan_RT_dfe" = "Spatial Span RT",
                              "rs_targetDetection_RT_dfe" = "Target Detection RT",
                              "rs_verbalAnalogies_RT_dfe" = "Verbal Analogies RT")
                              
         )

cogni_RT_control_dat <- cogni_RT_control_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks_RT),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_RT_dfe" = "2D Manipulations RT",
                              "rs_TOL_RT_dfe" = "TOL RT",
                              "rs_prospectiveMemoryWords_1_delayed_RT_dfe" = "Word Memory Delayed RT",
                              "rs_prospectiveMemoryWords_1_immediate_RT_dfe" = "Word Memory Immediate RT",
                              "rs_spatialSpan_RT_dfe" = "Spatial Span RT",
                              "rs_targetDetection_RT_dfe" = "Target Detection RT",
                              "rs_verbalAnalogies_RT_dfe" = "Verbal Analogies RT")
                              
         )
```


Violin plot cognitron tasks for cases only
```{r violin plot tasks cognitron cases}
pl4 <- ggplot(data = cogni_tasks_case_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl4 <- pl4 + geom_violin(trim = F)

pl4 <- pl4 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl4 <- pl4 + xlab("Task")

pl4 <- pl4 + scale_y_continuous(name = "Cognitron Task Score (DfE)",
                              breaks = seq(-10, 5, 2),
                              limits = c(-10, 5))

pl4 <- pl4 + labs(fill = "Task")

pl4 <- pl4 + scale_fill_brewer(palette = "Accent")

pl4 <- pl4 + theme_bw()

pl4 <- pl4 +
  ggtitle("Cognitron Score (DfE) for Cases by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl4

ggsave("plots/bytask/cognitron_bytask_cases_dfe_violplot.png")
```

Violin plot cognitron tasks for controls only
```{r violin plot tasks cognitron controls}
pl5 <- ggplot(data = cogni_tasks_control_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl5 <- pl5 + geom_violin(trim = F)

pl5 <- pl5 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl5 <- pl5 + xlab("Task")

pl5 <- pl5 + scale_y_continuous(name = "Cognitron Task Score (DfE)",
                              breaks = seq(-10, 5, 2),
                              limits = c(-10, 5))

pl5 <- pl5 + labs(fill = "Task")

pl5 <- pl5 + scale_fill_brewer(palette = "Accent")

pl5 <- pl5 + theme_bw()

pl5 <- pl5 +
  ggtitle("Cognitron Score (DfE) for Controls by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl5

ggsave("plots/bytask/cognitron_bytask_controls_dfe_violplot.png")
```

Violin plot cognitron RTs for cases only
```{r violin plot RTs cognitron cases}
pl6 <- ggplot(data = cogni_RT_case_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl6 <- pl6 + geom_violin(trim = F)

pl6 <- pl6 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl6 <- pl6 + xlab("Task")

pl6 <- pl6 + scale_y_continuous(name = "Cognitron RT (DfE)",
                              breaks = seq(-8, 30, 2),
                              limits = c(-8, 30))

pl6 <- pl6 + labs(fill = "Task")

pl6 <- pl6 + scale_fill_brewer(palette = "Accent")

pl6 <- pl6 + theme_bw()

pl6 <- pl6 +
  ggtitle("Cognitron RTs (DfE) for Cases by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl6

ggsave("plots/bytask/cognitron_bytaskRT_cases_dfe_violplot.png")
```

Violin plot cognitron RTs for controls only
```{r violin plot RTs cognitron controls}
pl7 <- ggplot(data = cogni_RT_control_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl7 <- pl7 + geom_violin(trim = F)

pl7 <- pl7 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl7 <- pl7 + xlab("Task")

pl7 <- pl7 + scale_y_continuous(name = "Cognitron RT (DfE)",
                              breaks = seq(-8, 30, 2),
                              limits = c(-8, 30))

pl7 <- pl7 + labs(fill = "Task")

pl7 <- pl7 + scale_fill_brewer(palette = "Accent")

pl7 <- pl7 + theme_bw()

pl7 <- pl7 +
  ggtitle("Cognitron RTs (DfE) for Controls by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl7

ggsave("plots/bytask/cognitron_bytaskRT_controls_dfe_violplot.png")
```

# Multiplots

Multiplot into single objects
```{r Multiplots}
pl8 <- cowplot::plot_grid(pl1, pl2, pl3, nrow = 1)
as.png(pl8, filename = "multiplots/cognitron_multiplot_diagscores.png" , width = 45, height = 15, scaled = TRUE)

pl9 <- cowplot::plot_grid(pl4, pl5)
as.png(pl9, filename = "multiplots/cognitron_multiplot_scores.png" , width = 30, height = 15, scaled = TRUE)

pl10 <- cowplot::plot_grid(pl6, pl7)
as.png(pl10, filename = "multiplots/cognitron_multiplot_RTs.png" , width = 30, height = 15, scaled = TRUE)
```
