---
title: "COVIDCNS Interim EDA Script"
author: "Zain Ahmad"
date: "24/06/2022"
output: html_document
---

**Deprecated**

Setup environment
```{r}
# Clear global environment
remove(list = ls())

# Import package_check
source(file = "functions/package_check.R")

# Install/load packages
packages <- c(
  "summarytools",
  "sjlabelled",
  "gtsummary",
  "cowplot",
  "plotscale",
  "tidyverse"
  )
package_check(packages)

# Import ilovecovidcns path
source(file = "credentials/paths.R")

# Import data
data_joined <- readRDS(file = paste0(ilovecovidcns, "/data/joined/covidcns_greta.rds"))

# Set gtsummary themes
theme_gtsummary_compact()
theme_gtsummary_journal("nejm")
```

Add windowed inpatient admission variable
```{r Window inpatient admission}
data_joined <- data_joined %>%
  mutate(
    ncrf1_admission_windowed =
      case_when(ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2020-03-01") & ncrf1_admission.date_of_inpatient_admission.txt <= as.POSIXct("2020-09-01")  ~ "March 2020 to August 2020",
                
                ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2020-09-01") & ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2021-03-01")  ~ "September 2020 to February 2021",
                
                ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2021-03-01") & ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2021-09-01")  ~ "March 2021 to August 2021",
                
                ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2021-09-01") & ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2022-03-01")  ~ "September 2021 to February 2022",
                is.na(ncrf1_admission.date_of_inpatient_admission.txt) ~ "Missing",
                ncrf1_admission.date_of_inpatient_admission.txt < as.POSIXct("2020-03-01") | ncrf1_admission.date_of_inpatient_admission.txt >= as.POSIXct("2022-03-01")  ~ "Other"
                )
    )
```

Simplify COVID19 severity
```{r Simplify severity}
data_joined <- data_joined %>%
  mutate(across(ncrf1_vital.admission_severity_worst_covid19,
                ~case_when(
        . == "Uninfected (No viral RNA detected)" ~ "Uninfected",
        . == "Asymptomatic (Viral RNA detected)" |
          . == "Symptomatic (Independent)"	|
          . == "Symptomatic (Assistance needed)" ~ "Ambulatory mild disease",
        . == "Hospitalised (No oxygen therapy)" |
          . == "Hospitalised (Oxygen by mask or nasal prongs)" ~ "Hospitalised: moderate disease",
        . == "Hospitalised (Oxygen by NIV or high flow)" |
          . == "Intubation and mechanical ventilation (pO2/FiO2 >= 150 or SpO2/FiO2 >= 200)" |
          . == "Mechanical ventilation (pO2/FiO2 <150 or SpO2/FiO2 <200 or vasopressors)" |
          . == "Mechanical ventilation (pO2/FiO2 <150 and vasopressors, dialysis or ECMO)" ~ "Hospitalised: severe disease",
        is.na(.) ~ NA_character_)
        )
    )
```




# Tables

## Summary Tables

Summary table by case control vaccine
```{r Summary table case control vaccine}
covidcns_sumtable <- data_joined %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Mutate windowed admission to ordered factor
  mutate(
    ncrf1_admission_windowed = 
      factor(
        ncrf1_admission_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   "Other",
                   "Missing"),
        ordered = TRUE
        )
    ) %>%
  
  # Convert NAs to explicit factor to show in table per category
  dplyr::mutate(dem.sex_at_birth = factor(dem.sex_at_birth) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_vital.admission_severity_worst_covid19 = factor(ncrf1_vital.admission_severity_worst_covid19) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf2_med.corticosteroid = factor(ncrf2_med.corticosteroid) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_comorbid.clinical_frailty_scale = factor(ncrf1_comorbid.clinical_frailty_scale) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.concerned_memory = factor(dem.concerned_memory) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.highest_education = factor(dem.highest_education) %>%
                  forcats::fct_explicit_na()) %>%
  
  # Create summary table
  tbl_summary(
    
    # split by case_control_vaccine
    by = case_control_vaccine,
              
    # vars to include
    include = c(dem.dob_age,
                dem.sex_at_birth,
                dem.highest_education,
                ncrf1_vital.admission_severity_worst_covid19,
                ncrf1_comorbid.clinical_frailty_scale,
                ncrf1_admission_windowed,
                gad7.sum_score,
                phq9.sum_score,
                pcl5.sum_score,
                ncrf2_med.corticosteroid,
                dem.concerned_memory,
                Composite_global,
                Composite_acc,
                Composite_rt),
    
    # 2 line summary
    type = all_continuous() ~ "continuous2",
    
    # exclude standard missing values
    missing = "no",
    
    # add mean, sd, missing n and missing % for cont vars
    statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
    
    # add custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 ncrf1_admission_windowed ~ "Date of Inpatient Admission",
                 gad7.sum_score ~ "GAD7 Sumscore (Cutoff = 10)",
                 phq9.sum_score ~ "PHQ9 Sumscore (Cutoff = 10)",
                 pcl5.sum_score ~ "PCL5 Sumscore (Cutoff = 32)",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory",
                 Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
              ) %>%
  
  # add labels for missing n/%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  
  # bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_sumtable), file = "analysis/tables/summary/covidcns_sumtable.png")

# View table
covidcns_sumtable
```

Summary table by diagnostic group
```{r Summary table diagnostic group}
covidcns_sumtable_bycase <- data_joined %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Mutate windowed admission to ordered factor
  mutate(
    ncrf1_admission_windowed = 
      factor(
        ncrf1_admission_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   "Other",
                   "Missing"),
        ordered = TRUE
        )
    ) %>%
  
  # Convert NAs to explicit factor to show in table per category
  dplyr::mutate(dem.sex_at_birth = factor(dem.sex_at_birth) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_vital.admission_severity_worst_covid19 = factor(ncrf1_vital.admission_severity_worst_covid19) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf2_med.corticosteroid = factor(ncrf2_med.corticosteroid) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_comorbid.clinical_frailty_scale = factor(ncrf1_comorbid.clinical_frailty_scale) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.concerned_memory = factor(dem.concerned_memory) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.highest_education = factor(dem.highest_education) %>%
                  forcats::fct_explicit_na()) %>%
  
  # Create summary table with stats to match Kuha's table
  tbl_summary(by = diagnostic_group, # same as above except this line
              include = c(dem.dob_age,
                          dem.sex_at_birth,
                          dem.highest_education,
                          ncrf1_vital.admission_severity_worst_covid19,
                          ncrf1_comorbid.clinical_frailty_scale,
                          ncrf1_admission_windowed,
                          gad7.sum_score,
                          phq9.sum_score,
                          pcl5.sum_score,
                          ncrf2_med.corticosteroid,
                          dem.concerned_memory,
                          Composite_global,
                          Composite_acc,
                          Composite_rt),
              type = all_continuous() ~ "continuous2",
              missing = "no",
              statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
              label = list(dem.dob_age ~ "Age",
                           dem.sex_at_birth ~ "Sex",
                           dem.highest_education ~ "Education",
                           ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                           ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                           ncrf1_admission_windowed ~ "Date of Inpatient Admission",
                           gad7.sum_score ~ "GAD7 Sumscore (Cutoff = 10)",
                           phq9.sum_score ~ "PHQ9 Sumscore (Cutoff = 10)",
                           pcl5.sum_score ~ "PCL5 Sumscore (Cutoff = 32)",
                           ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                           dem.concerned_memory ~ "Concerned about Memory",
                           Composite_global ~ "Cognitron Global Score",
                           Composite_acc ~ "Cognitron Accuracy Score",
                           Composite_rt ~ "Cognitron RT Score")
              ) %>%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  bold_labels()

# Save table
gt::gtsave(as_gt(covidcns_sumtable_bycase), file = "analysis/tables/summary/covidcns_sumtable_bycase.png")
covidcns_sumtable_bycase
```


## Regression Tables


Multivariate regression table global scores
```{r Regression table global}
covidcns_regtable_global <- data_joined %>%

  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Select regression vars
  select(Composite_global,
         dem.dob_age,
         dem.sex_at_birth,
         dem.highest_education,
         diagnostic_group,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_comorbid.clinical_frailty_scale,
         gad7.sum_score,
         phq9.sum_score,
         pcl5.sum_score,
         cfs.sum_score,
         case_control_vaccine,
         ncrf2_med.corticosteroid,
         dem.concerned_memory
         ) %>%
  
  # Relevel 
  mutate(diagnostic_group = relevel(as.factor(diagnostic_group), ref = "Unknown")) %>%
  
  # Regression table
  tbl_uvregression(
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_global,
    
    # set custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 diagnostic_group ~ "Clinical Group",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 gad7.sum_score ~ "GAD7 Sumscore",
                 phq9.sum_score ~ "PHQ9 Sumscore",
                 pcl5.sum_score ~ "PCL5 Sumscore",
                 cfs.sum_score ~ "CFS Sumscore",
                 case_control_vaccine ~ "Case/Control/Vaccine status",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory"),
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_global), file = "analysis/tables/regression/covidcns_regtable_global.png")

# View table
covidcns_regtable_global
```

Multivariate regression table accuracy scores
```{r Regression table accuracy}
covidcns_regtable_accuracy <- data_joined %>%

  # Remove pts missing cognitron
  filter(!is.na(Composite_acc)) %>%
  
  # Select regression vars
  select(Composite_acc,
         dem.dob_age,
         dem.sex_at_birth,
         dem.highest_education,
         diagnostic_group,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_comorbid.clinical_frailty_scale,
         gad7.sum_score,
         phq9.sum_score,
         pcl5.sum_score,
         cfs.sum_score,
         case_control_vaccine,
         ncrf2_med.corticosteroid,
         dem.concerned_memory
         ) %>%
  
  # Regression table
  tbl_uvregression(
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_acc,
    
    # set custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 diagnostic_group ~ "Clinical Group",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 gad7.sum_score ~ "GAD7 Sumscore",
                 phq9.sum_score ~ "PHQ9 Sumscore",
                 pcl5.sum_score ~ "PCL5 Sumscore",
                 cfs.sum_score ~ "CFS Sumscore",
                 case_control_vaccine ~ "Case/Control/Vaccine status",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory"),
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_accuracy), file = "analysis/tables/regression/covidcns_regtable_accuracy.png")

# View table
covidcns_regtable_accuracy
```

Multivariate regression table RTs
```{r Regression table RTs}
covidcns_regtable_rt <- data_joined %>%

  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Select regression vars
  select(Composite_rt,
         dem.dob_age,
         dem.sex_at_birth,
         dem.highest_education,
         diagnostic_group,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_comorbid.clinical_frailty_scale,
         gad7.sum_score,
         phq9.sum_score,
         pcl5.sum_score,
         cfs.sum_score,
         case_control_vaccine,
         ncrf2_med.corticosteroid,
         dem.concerned_memory
         ) %>%
  
  # Regression table
  tbl_uvregression(
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_rt,
    
    # set custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 diagnostic_group ~ "Clinical Group",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 gad7.sum_score ~ "GAD7 Sumscore",
                 phq9.sum_score ~ "PHQ9 Sumscore",
                 pcl5.sum_score ~ "PCL5 Sumscore",
                 cfs.sum_score ~ "CFS Sumscore",
                 case_control_vaccine ~ "Case/Control/Vaccine status",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory"),
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_rt), file = "analysis/tables/regression/covidcns_regtable_rt.png")

# View table
covidcns_regtable_rt
```



## ANOVA


ANOVA table for cognitron dfe scores by case/control/vaccine
```{r ANOVA case control vaccine}
covidcns_anovatable_ccv <- data_joined %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Summary table
  tbl_summary(
    by = case_control_vaccine,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "aov"))

# Save table as png image
gt::gtsave(as_gt(covidcns_anovatable_ccv), file = "analysis/tables/anova/covidcns_anovatable_ccv.png")

# View table
covidcns_anovatable_ccv
```

ANOVA table for cognitron dfe scores by diagnostic group
```{r ANOVA diag group}
covidcns_anovatable_diag <- data_joined %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Summary table
  tbl_summary(
    by = diagnostic_group,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "aov"))

# Save table as png image
gt::gtsave(as_gt(covidcns_anovatable_diag), file = "analysis/tables/anova/covidcns_anovatable_diag.png")

# View table
covidcns_anovatable_diag
```



## T Test Tables

T-test table for cognitron dfe scores by case/control/vaccine
```{r T tesst case control vaccine}
covidcns_ttesttable_ccv <- data_joined %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   . == "Control: COVID-19 negative (e.g. pneumonia, sepsis)" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Summary table
  tbl_summary(
    by = case_control_vaccine,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "t.test"))

# Save table as png image
gt::gtsave(as_gt(covidcns_ttesttable_ccv), file = "analysis/tables/ttest/covidcns_ttesttable_ccv.png")

# View table
covidcns_ttesttable_ccv
```


T-test table for cognitron dfe scores by case/control/vaccine
```{r T tesst case control vaccine}
covidcns_ttesttable1_ccv <- data_joined %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   . == "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Summary table
  tbl_summary(
    by = case_control_vaccine,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "t.test"))

# Save table as png image
gt::gtsave(as_gt(covidcns_ttesttable1_ccv), file = "analysis/tables/ttest/covidcns_ttesttable1_ccv.png")

# View table
covidcns_ttesttable1_ccv
```


## Correlations


Correlation Matrix and Plot
```{r Correlation matrix of all variables}
corr_dat <- data_joined %>%
  select(
    `Age` = "dem.dob_age",
    `Sex` = "dem.sex_at_birth_numeric",
    `Memory Concerns` = "dem.concerned_memory_numeric",
    `Education` = "dem.highest_education_numeric",
    `COVID19 Severity` = "ncrf1_vital.admission_severity_worst_covid19_numeric",
    `Clinical Frailty` = "ncrf1_comorbid.clinical_frailty_scale_numeric",
    `GAD7` = "gad7.sum_score",
    `PHQ9` = "phq9.sum_score",
    `PCL5` = "pcl5.sum_score",
    `CFS` = "cfs.sum_score",
    `Corticosteroids` = "ncrf2_med.corticosteroid_numeric"
 ) 

corr_out <- psych::mixedCor(data = corr_dat,
                            c = c(1,3:11),
                            d = c(2),
                            use = "pairwise.complete.obs")

corr_out_rmat <- corr_out$rho


# Write file path to save plot
png(file = "analysis/correlations/corr_matrix.png")
# Create correlation matrix with hierarchical clustering
corr_matrix_plot <- corrplot::corrplot(corr_out_rmat, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 1,
         cl.cex = 1,
         order = "original",
         tl.col = "black",
         cl.align.text = "c",
         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         number.font = 0.5,
         number.cex = 0.5, # size of co-efficients
         sig.level = 0.01, # Choose significant level
         insig = "blank", # Nonsignificant correlations have no colour,
         bg = "white"
         )
# Save plot
dev.off()

```


# Plots


# Plots of Composite Scores


Violin plot cognitron global by diagnostic group
```{r violin plot global cognitron}
pl1 <- ggplot(
  data = subset(data_joined,!is.na(diagnostic_group) & !is.na(Composite_global)), # remove NAs from plotting vars
  aes(x = diagnostic_group, y = Composite_global, fill = diagnostic_group) # plot and fill by diag group
  )

# violin plot
pl1 <- pl1 + geom_violin(trim = F)

# add summary stat line
pl1 <- pl1 + stat_summary(fun.data=mean_sdl, # can use median_hilow instead
                          geom="pointrange",
                          color="cyan")

pl1 <- pl1 + xlab("Diagnostic Group")

pl1 <- pl1 + ylab("Cognitron Global Score (DfE)")

pl1 <- pl1 + labs(fill = "Diagnostic Group")

pl1 <- pl1 + scale_fill_brewer(palette = "Accent")

pl1 <- pl1 + theme_bw()

pl1 <- pl1 + 
  ggtitle("Cognitron Global Score (DfE) by Diagnostic Group in the COVIDCNS Study") + 
  theme(plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl1

ggsave("analysis/plots/bydiagnosis/cognitron_global_bydiag_violplot.png")
```


Violin plot cognitron accuracy by diagnostic group
```{r violin plot acc cognitron}
pl2 <- ggplot(data = subset(data_joined,
                            !is.na(diagnostic_group) &
                              !is.na(Composite_acc)),
              aes(x = diagnostic_group,
                  y = Composite_acc,
                  fill = diagnostic_group))

pl2 <- pl2 + geom_violin(trim = F)

pl2 <- pl2 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl2 <- pl2 + xlab("Diagnostic Group")

pl2 <- pl2 + ylab("Cognitron Accuracy Score (DfE)")

pl2 <- pl2 + labs(fill = "Diagnostic Group")

pl2 <- pl2 + scale_fill_brewer(palette = "Accent")

pl2 <- pl2 + theme_bw()

pl2 <- pl2 +
  ggtitle("Cognitron Accuracy Score (DfE) by Diagnostic Group in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl2

ggsave("analysis/plots/bydiagnosis/cognitron_acc_bydiag_violplot.png")
```

Violin plot cognitron RT by diagnostic group
```{r violin plot rt cognitron}
pl3 <- ggplot(data = subset(data_joined,
                            !is.na(diagnostic_group) &
                              !is.na(Composite_rt)),
              aes(x = diagnostic_group,
                  y = Composite_rt,
                  fill = diagnostic_group))

pl3 <- pl3 + geom_violin(trim = F)

pl3 <- pl3 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl3 <- pl3 + xlab("Diagnostic Group")

pl3 <- pl3 + ylab("Cognitron RT Score (DfE)")

pl3 <- pl3 + labs(fill = "Diagnostic Group")

pl3 <- pl3 + scale_fill_brewer(palette = "Accent")

pl3 <- pl3 + theme_bw()

pl3 <- pl3 + 
  ggtitle("Cognitron RT Score (DfE) by Diagnostic Group in the COVIDCNS Study") + 
  theme(plot.title = element_text(hjust = 0),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl3

ggsave("analysis/plots/bydiagnosis/cognitron_rt_bydiag_violplot.png")
```


# Plots by Task


Create vectors of cognitron task colnames
```{r Vectors cognitron tasks}
cogni_cols_demographics <- c(
  "age1",
  "age2",
  "decade",
  "sex",
  "language",
  "education",
  "DEVICE"
)

cogni_cols_tasks <- c(
  "rs_prospectiveMemoryWords_1_immediate",
  "rs_spatialSpan",
  "rs_manipulations2D",
  "rs_verbalAnalogies",
  "rs_prospectiveMemoryWords_1_delayed",
  "rs_TOL",
  "rs_targetDetection"
)

cogni_cols_tasks_RT <- c(
  "rs_prospectiveMemoryWords_1_immediate_RT",
  "rs_spatialSpan_RT",
  "rs_manipulations2D_RT",
  "rs_verbalAnalogies_RT",
  "rs_prospectiveMemoryWords_1_delayed_RT",
  "rs_TOL_RT",
  "rs_targetDetection_RT"
)

cogni_cols_dfe_tasks <- c(
  "rs_manipulations2D_dfe",
  "rs_TOL_dfe",
  "rs_prospectiveMemoryWords_1_delayed_dfe",
  "rs_prospectiveMemoryWords_1_immediate_dfe",
  "rs_spatialSpan_dfe",
  "rs_targetDetection_dfe",
  "rs_verbalAnalogies_dfe"
)

cogni_cols_dfe_tasks_RT <- c(
  "rs_manipulations2D_RT_dfe",
  "rs_TOL_RT_dfe",
  "rs_prospectiveMemoryWords_1_delayed_RT_dfe",
  "rs_prospectiveMemoryWords_1_immediate_RT_dfe",
  "rs_spatialSpan_RT_dfe",
  "rs_targetDetection_RT_dfe",
  "rs_verbalAnalogies_RT_dfe"
)

cogni_tasks_dat <- data_joined %>%
  select(
    all_of(
      cogni_cols_dfe_tasks
    )
  )

cogni_RT_dat <- data_joined %>%
  select(
    all_of(
      cogni_cols_dfe_tasks_RT
    )
  )
```

Subset tasks and RTs by case and control for plotting
```{r Subset tasks RTs case control}
cogni_tasks_case_dat <- data_joined %>%
  filter(case_control_vaccine == "Case: COVID-19 positive (i.e. neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks
    )
  )

cogni_tasks_control_dat <- data_joined %>%
  filter(case_control_vaccine == "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks
    )
  )

cogni_RT_case_dat <- data_joined %>%
  filter(case_control_vaccine == "Case: COVID-19 positive (i.e. neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks_RT
    )
  )

cogni_RT_control_dat <- data_joined %>%
  filter(case_control_vaccine == "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)") %>%
  select(
    all_of(
      cogni_cols_dfe_tasks_RT
    )
  )
```


Transform cognitron tasks wide to long to plot by task
```{r Transform wide long}
cogni_tasks_case_dat <- cogni_tasks_case_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_dfe" = "2D Manipulations",
                              "rs_TOL_dfe" = "TOL",
                              "rs_prospectiveMemoryWords_1_delayed_dfe" = "Word Memory Delayed",
                              "rs_prospectiveMemoryWords_1_immediate_dfe" = "Word Memory Immediate",
                              "rs_spatialSpan_dfe" = "Spatial Span",
                              "rs_targetDetection_dfe" = "Target Detection",
                              "rs_verbalAnalogies_dfe" = "Verbal Analogies")
                              
         )

cogni_tasks_control_dat <- cogni_tasks_control_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_dfe" = "2D Manipulations",
                              "rs_TOL_dfe" = "TOL",
                              "rs_prospectiveMemoryWords_1_delayed_dfe" = "Word Memory Delayed",
                              "rs_prospectiveMemoryWords_1_immediate_dfe" = "Word Memory Immediate",
                              "rs_spatialSpan_dfe" = "Spatial Span",
                              "rs_targetDetection_dfe" = "Target Detection",
                              "rs_verbalAnalogies_dfe" = "Verbal Analogies")
                              
         )

cogni_RT_case_dat <- cogni_RT_case_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks_RT),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_RT_dfe" = "2D Manipulations RT",
                              "rs_TOL_RT_dfe" = "TOL RT",
                              "rs_prospectiveMemoryWords_1_delayed_RT_dfe" = "Word Memory Delayed RT",
                              "rs_prospectiveMemoryWords_1_immediate_RT_dfe" = "Word Memory Immediate RT",
                              "rs_spatialSpan_RT_dfe" = "Spatial Span RT",
                              "rs_targetDetection_RT_dfe" = "Target Detection RT",
                              "rs_verbalAnalogies_RT_dfe" = "Verbal Analogies RT")
                              
         )

cogni_RT_control_dat <- cogni_RT_control_dat %>%
  drop_na() %>%
  tidyr::pivot_longer(
    cols = all_of(cogni_cols_dfe_tasks_RT),
    names_to = "task"
  ) %>%
  mutate(task = as.factor(task)) %>%
  mutate(task = recode_factor(task,
                              "rs_manipulations2D_RT_dfe" = "2D Manipulations RT",
                              "rs_TOL_RT_dfe" = "TOL RT",
                              "rs_prospectiveMemoryWords_1_delayed_RT_dfe" = "Word Memory Delayed RT",
                              "rs_prospectiveMemoryWords_1_immediate_RT_dfe" = "Word Memory Immediate RT",
                              "rs_spatialSpan_RT_dfe" = "Spatial Span RT",
                              "rs_targetDetection_RT_dfe" = "Target Detection RT",
                              "rs_verbalAnalogies_RT_dfe" = "Verbal Analogies RT")
                              
         )
```


Violin plot cognitron tasks for cases only
```{r violin plot tasks cognitron cases}
pl4 <- ggplot(data = cogni_tasks_case_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl4 <- pl4 + geom_violin(trim = F)

pl4 <- pl4 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl4 <- pl4 + xlab("Task")

pl4 <- pl4 + scale_y_continuous(name = "Cognitron Task Score (DfE)",
                              breaks = seq(-10, 5, 2),
                              limits = c(-10, 5))

pl4 <- pl4 + labs(fill = "Task")

pl4 <- pl4 + scale_fill_brewer(palette = "Accent")

pl4 <- pl4 + theme_bw()

pl4 <- pl4 +
  ggtitle("Cognitron Score (DfE) for Cases by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl4

ggsave("analysis/plots/bytask/cognitron_bytask_cases_dfe_violplot.png")
```

Violin plot cognitron tasks for controls only
```{r violin plot tasks cognitron controls}
pl5 <- ggplot(data = cogni_tasks_control_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl5 <- pl5 + geom_violin(trim = F)

pl5 <- pl5 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl5 <- pl5 + xlab("Task")

pl5 <- pl5 + scale_y_continuous(name = "Cognitron Task Score (DfE)",
                              breaks = seq(-10, 5, 2),
                              limits = c(-10, 5))

pl5 <- pl5 + labs(fill = "Task")

pl5 <- pl5 + scale_fill_brewer(palette = "Accent")

pl5 <- pl5 + theme_bw()

pl5 <- pl5 +
  ggtitle("Cognitron Score (DfE) for Controls by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl5

ggsave("analysis/plots/bytask/cognitron_bytask_controls_dfe_violplot.png")
```

Violin plot cognitron RTs for cases only
```{r violin plot RTs cognitron cases}
pl6 <- ggplot(data = cogni_RT_case_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl6 <- pl6 + geom_violin(trim = F)

pl6 <- pl6 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl6 <- pl6 + xlab("Task")

pl6 <- pl6 + scale_y_continuous(name = "Cognitron RT (DfE)",
                              breaks = seq(-8, 30, 2),
                              limits = c(-8, 30))

pl6 <- pl6 + labs(fill = "Task")

pl6 <- pl6 + scale_fill_brewer(palette = "Accent")

pl6 <- pl6 + theme_bw()

pl6 <- pl6 +
  ggtitle("Cognitron RTs (DfE) for Cases by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl6

ggsave("analysis/plots/bytask/cognitron_bytaskRT_cases_dfe_violplot.png")
```

Violin plot cognitron RTs for controls only
```{r violin plot RTs cognitron controls}
pl7 <- ggplot(data = cogni_RT_control_dat,
              aes(x = task,
                  y = value,
                  fill = task))

pl7 <- pl7 + geom_violin(trim = F)

pl7 <- pl7 + stat_summary(fun.data=mean_sdl,
                          geom="pointrange",
                          color="cyan")

pl7 <- pl7 + xlab("Task")

pl7 <- pl7 + scale_y_continuous(name = "Cognitron RT (DfE)",
                              breaks = seq(-8, 30, 2),
                              limits = c(-8, 30))

pl7 <- pl7 + labs(fill = "Task")

pl7 <- pl7 + scale_fill_brewer(palette = "Accent")

pl7 <- pl7 + theme_bw()

pl7 <- pl7 +
  ggtitle("Cognitron RTs (DfE) for Controls by Task in the COVIDCNS Study") +
  theme(plot.title = element_text(hjust = 0),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

pl7

ggsave("analysis/plots/bytask/cognitron_bytaskRT_controls_dfe_violplot.png")
```

# Multiplots

Multiplot into single objects
```{r Multiplots}
pl8 <- cowplot::plot_grid(pl1, pl2, pl3, nrow = 1)
as.png(pl8, filename = "analysis/multiplots/cognitron_multiplot_diagscores.png" , width = 45, height = 15, scaled = TRUE)

pl9 <- cowplot::plot_grid(pl4, pl5)
as.png(pl9, filename = "analysis/multiplots/cognitron_multiplot_scores.png" , width = 30, height = 15, scaled = TRUE)

pl10 <- cowplot::plot_grid(pl6, pl7)
as.png(pl10, filename = "analysis/multiplots/cognitron_multiplot_RTs.png" , width = 30, height = 15, scaled = TRUE)
```
