---
title: "COVIDCNS Cognitive Analysis Regressions"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

## Regression Tables


Multivariate regression table global scores
```{r Regression table global}
covidcns_regtable_global <- dat %>%

  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Select regression vars
  select(Composite_global,
         dem.dob_age,
         dem.sex_at_birth,
         dem.highest_education,
         diagnostic_group,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_comorbid.clinical_frailty_scale,
         gad7.sum_score,
         phq9.sum_score,
         pcl5.sum_score,
         cfs.sum_score,
         case_control_vaccine,
         ncrf2_med.corticosteroid,
         dem.concerned_memory
         ) %>%
  
  # Relevel 
  mutate(diagnostic_group = relevel(as.factor(diagnostic_group), ref = "Unknown")) %>%
  
  # Regression table
  tbl_uvregression(
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_global,
    
    # set custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 diagnostic_group ~ "Clinical Group",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 gad7.sum_score ~ "GAD7 Sumscore",
                 phq9.sum_score ~ "PHQ9 Sumscore",
                 pcl5.sum_score ~ "PCL5 Sumscore",
                 cfs.sum_score ~ "CFS Sumscore",
                 case_control_vaccine ~ "Case/Control/Vaccine status",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory"),
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_global),
           file = paste0(ilovecovidcns, "/tables/regression/covidcns_regtable_global.png"))

# View table
covidcns_regtable_global
```

Multivariate regression table accuracy scores
```{r Regression table accuracy}
covidcns_regtable_accuracy <- dat %>%

  # Remove pts missing cognitron
  filter(!is.na(Composite_acc)) %>%
  
  # Select regression vars
  select(Composite_acc,
         dem.dob_age,
         dem.sex_at_birth,
         dem.highest_education,
         diagnostic_group,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_comorbid.clinical_frailty_scale,
         gad7.sum_score,
         phq9.sum_score,
         pcl5.sum_score,
         cfs.sum_score,
         case_control_vaccine,
         ncrf2_med.corticosteroid,
         dem.concerned_memory
         ) %>%
  
  # Regression table
  tbl_uvregression(
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_acc,
    
    # set custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 diagnostic_group ~ "Clinical Group",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 gad7.sum_score ~ "GAD7 Sumscore",
                 phq9.sum_score ~ "PHQ9 Sumscore",
                 pcl5.sum_score ~ "PCL5 Sumscore",
                 cfs.sum_score ~ "CFS Sumscore",
                 case_control_vaccine ~ "Case/Control/Vaccine status",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory"),
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_accuracy),
           file = paste0(ilovecovidcns, "/tables/regression/covidcns_regtable_accuracy.png"))

# View table
covidcns_regtable_accuracy
```

Multivariate regression table RTs
```{r Regression table RTs}
covidcns_regtable_rt <- dat %>%

  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Select regression vars
  select(Composite_rt,
         dem.dob_age,
         dem.sex_at_birth,
         dem.highest_education,
         diagnostic_group,
         ncrf1_vital.admission_severity_worst_covid19,
         ncrf1_comorbid.clinical_frailty_scale,
         gad7.sum_score,
         phq9.sum_score,
         pcl5.sum_score,
         cfs.sum_score,
         case_control_vaccine,
         ncrf2_med.corticosteroid,
         dem.concerned_memory
         ) %>%
  
  # Regression table
  tbl_uvregression(
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_rt,
    
    # set custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 diagnostic_group ~ "Clinical Group",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 gad7.sum_score ~ "GAD7 Sumscore",
                 phq9.sum_score ~ "PHQ9 Sumscore",
                 pcl5.sum_score ~ "PCL5 Sumscore",
                 cfs.sum_score ~ "CFS Sumscore",
                 case_control_vaccine ~ "Case/Control/Vaccine status",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory"),
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_rt),
           file = paste0(ilovecovidcns, "/tables/regression/covidcns_regtable_rt.png"))

# View table
covidcns_regtable_rt
```
