---
title: "COVIDCNS Cognitive Analysis Regressions"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

```{r}
table_subset <- dat %>%
  select(
    # sample level grouping
    case_control_vaccine,
    diagnostic_group,
    # demographics
    dem.dob_age,
    dem.sex_at_birth,
    dem.highest_education,
    dem.is_english_your_first_language,
    # demographics memory questions
    dem.concerned_memory,
    dem.concerned_memory_before_covid,
    dem.concerned_memory_after_covid,
    dem.memory_problem_worse_year,
    dem.has_your_memory_got_progressively_worse,
    # mh questionnaires
    gad7.sum_score,
    gad7.binary_clinical,
    phq9.sum_score,
    phq9.binary_depression,
    pcl5.sum_score,
    pcl5.binary_PTSD,
    cfs.sum_score,
    cfs.mental_subscale,
    cfs.physical_subscale,
    # ncrf data
    ncrf1_vital.admission_severity_worst_covid19,
    ncrf1_pre_med.had_covid19_vaccine,
    ncrf1_comorbid.clinical_frailty_scale,
    ncrf1_admission.inpatient_admission_windowed,
    ncrf1_admission.covid_test_windowed,
    ncrf1_lab.crp,
    ncrf1_lab.crp_level,
    ncrf1_lab.wbc_count,
    ncrf1_lab.wbc_count_level,
    ncrf2_lab.crp,
    ncrf2_lab.crp_level,
    ncrf2_lab.wbc_count,
    ncrf2_lab.wbc_count_level,
    ncrf2_med.corticosteroid,
    # cognitron composites
    Composite_global,
    Composite_acc,
    Composite_rt
  ) %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Relevel 
  mutate(diagnostic_group = relevel(as.factor(diagnostic_group), ref = "Control")) %>%
  mutate(case_control_vaccine = relevel(as.factor(case_control_vaccine), ref = "Control: COVID-19 negative (e.g. pneumonia, sepsis)")) %>%
  mutate(ncrf1_vital.admission_severity_worst_covid19 = relevel(as.factor(ncrf1_vital.admission_severity_worst_covid19), ref = "Uninfected")) %>%
  mutate(ncrf1_pre_med.had_covid19_vaccine = relevel(as.factor(ncrf1_pre_med.had_covid19_vaccine), ref = "No")) %>%
  mutate(ncrf2_med.corticosteroid = relevel(as.factor(ncrf2_med.corticosteroid), ref = "No"))
```

Create list of labels
```{r Create label list}
dat_label_list <- list(
  # sample level groupings
  case_control_vaccine ~ "Case Status",
  diagnostic_group ~ "Diagnostic Group",
  # demographics
  dem.dob_age ~ "Age",
  dem.sex_at_birth ~ "Sex",
  dem.highest_education ~ "Education",
  dem.is_english_your_first_language ~ "English as First Language",
  # demographics memory questions
  dem.concerned_memory ~ "Concerned about Memory",
  dem.concerned_memory_before_covid ~ "Concerned about Memory before COVID",
  dem.concerned_memory_after_covid ~ "Concerned about Memory after COVID",
  dem.memory_problem_worse_year ~ "Memory problem worsened in last year",
  dem.has_your_memory_got_progressively_worse ~ "Memory problem progressively worsening",
  # mh questionnaires
  gad7.sum_score ~ "GAD7 Sumscore (Cutoff = 10)",
  gad7.binary_clinical ~ "GAD7 Algorithmic Diagnosis",
  phq9.sum_score ~ "PHQ9 Sumscore (Cutoff = 10)",
  phq9.binary_depression ~ "PHQ9 Algorithmic Diagnosis",
  pcl5.sum_score ~ "PCL5 Sumscore (Cutoff = 32)",
  pcl5.binary_PTSD ~ "PCL5 Algorithmic Diagnosis",
  cfs.sum_score ~ "Chalder Fatigue Sumscore",
  cfs.mental_subscale ~ "Mental Fatigue",
  cfs.physical_subscale ~ "Physical Fatigue",
  # ncrf data
  ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
  ncrf1_pre_med.had_covid19_vaccine ~ "Had COVID19 Vaccine?",
  ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
  ncrf1_admission.inpatient_admission_windowed ~ "Date of Inpatient Admission",
  ncrf1_admission.covid_test_windowed ~ "Date of Positive COVID19 Test",
  ncrf1_lab.crp ~ "CRP (Module 1)",
  ncrf1_lab.crp_level ~ "CRP Level (Module 1)",
  ncrf1_lab.wbc_count ~ "White Cell Count (Module 1)",
  ncrf1_lab.wbc_count_level ~ "White Cell Count Level (Module 1)",
  ncrf2_lab.crp ~ "CRP (Module 2)",
  ncrf2_lab.crp_level ~ "CRP Level (Module 2)",
  ncrf2_lab.wbc_count ~ "White Cell Count (Module 2)",
  ncrf2_lab.wbc_count_level ~ "White Cell Count Level (Module 2)",
  ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
  # cognitron composites
  Composite_global ~ "Cognitron Global Score",
  Composite_acc ~ "Cognitron Accuracy Score",
  Composite_rt ~ "Cognitron RT Score"
      )
```



## Regression Tables


Multivariate regression table global scores
```{r Regression table global}
covidcns_regtable_global <- table_subset %>%
  
  # Regression table
  tbl_uvregression(
    
    # Exclude cognitron scores 
    include = c(
      -Composite_acc,
      -Composite_rt
    ),
    
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_global,
    
    # set custom labels
    label = dat_label_list,
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_global),
           file = paste0(ilovecovidcns, "/tables/regression/covidcns_regtable_global.png"))

# View table
covidcns_regtable_global
```

Multivariate regression table accuracy scores
```{r Regression table accuracy}
covidcns_regtable_accuracy <- table_subset %>%

  # Regression table
  tbl_uvregression(
    
    # Exclude cognitron scores 
    include = c(
      -Composite_global,
      -Composite_rt
    ),
    
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_acc,
    
    # set custom labels
    label = dat_label_list,
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_accuracy),
           file = paste0(ilovecovidcns, "/tables/regression/covidcns_regtable_accuracy.png"))

# View table
covidcns_regtable_accuracy
```

Multivariate regression table RTs
```{r Regression table RTs}
covidcns_regtable_rt <- table_subset %>%
  
  # Regression table
  tbl_uvregression(
    
    # Exclude cognitron scores 
    include = c(
      -Composite_global,
      -Composite_acc
    ),
    
    # linear regression
    method = lm,
    
    # outcome cognitron global score
    y = Composite_rt,
    
    # set custom labels
    label = dat_label_list,
    
    # zero estimates for 1st category in categorical vars
    add_estimate_to_reference_rows = TRUE
  ) %>%
  
  # add bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_regtable_rt),
           file = paste0(ilovecovidcns, "/tables/regression/covidcns_regtable_rt.png"))

# View table
covidcns_regtable_rt
```
