---
title: "COVIDCNS Cognitive Analysis Statistical Tests"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
theme_gtsummary_compact()
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

## ANOVA


ANOVA table for cognitron dfe scores by case/control/vaccine
```{r ANOVA case control vaccine}
covidcns_anovatable_ccv <- dat %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Summary table
  tbl_summary(
    by = case_control_vaccine,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "aov"))

# Save table as png image
gt::gtsave(as_gt(covidcns_anovatable_ccv),
           file = paste0(ilovecovidcns, "/tables/anova/covidcns_anovatable_ccv.png"))

# View table
covidcns_anovatable_ccv
```

ANOVA table for cognitron dfe scores by diagnostic group
```{r ANOVA diag group}
covidcns_anovatable_diag <- dat %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Summary table
  tbl_summary(
    by = diagnostic_group,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "aov"))

# Save table as png image
gt::gtsave(as_gt(covidcns_anovatable_diag),
           file = paste0(ilovecovidcns, "/tables/anova/covidcns_anovatable_diag.png"))

# View table
covidcns_anovatable_diag
```



## T Test Tables

T-test table for cognitron dfe scores by case/control/vaccine
```{r T tesst case control vaccine}
covidcns_ttesttable_ccv <- dat %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   . == "Control: COVID-19 negative (e.g. pneumonia, sepsis)" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Summary table
  tbl_summary(
    by = case_control_vaccine,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "t.test"))

# Save table as png image
gt::gtsave(as_gt(covidcns_ttesttable_ccv),
           file = paste0(ilovecovidcns, "/tables/ttest/covidcns_ttesttable_ccv.png"))

# View table
covidcns_ttesttable_ccv
```


T-test table for cognitron dfe scores by case/control/vaccine
```{r T tesst case control vaccine}
covidcns_ttesttable1_ccv <- dat %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_rt)) %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   . == "Control: COVID-19 positive (i.e. NO neurological or psychiatric complication)" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Summary table
  tbl_summary(
    by = case_control_vaccine,
    include = c(Composite_global, Composite_acc, Composite_rt),
    statistic = list(all_continuous() ~ c("{mean} ({sd})")),
    label = list(Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
  ) %>%
  
  # Add one-way ANOVA
  add_p(list(everything() ~ "t.test"))

# Save table as png image
gt::gtsave(as_gt(covidcns_ttesttable1_ccv),
           file = paste0(ilovecovidcns, "/tables/ttest/covidcns_ttesttable1_ccv.png"))

# View table
covidcns_ttesttable1_ccv
```
