---
title: "COVIDCNS Steering Group Data Table and Visualisation Script"
author: "Zain Ahmad"
date: '2022-07-12'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "cowplot",
              "plotscale",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

Create subset of data to table
```{r Subset for table}
table_subset <- dat %>%
  select(
    # sample level groupings
    case_control_vaccine,
    # baseline demographics
    dem.dob_age,
    dem.sex_at_birth,
    dem.highest_education,
    dem.is_english_your_first_language,
    dem.simplified_ethnicity,
    impact.current_employment_status,
    # ncrf data
    ncrf1_vital.admission_severity_worst_covid19,
    ncrf1_comorbid.clinical_frailty_scale,
    ncrf1_admission.inpatient_admission_windowed
  ) %>%
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   str_detect(case_control_vaccine, "ontrol") ~ "Control",
                                   str_detect(case_control_vaccine, "ase") ~ "Case",
                                   TRUE ~ .)
                )
          ) %>%
  
  # Mutate windowed admission to ordered factor
  mutate(
    ncrf1_admission.inpatient_admission_windowed = 
      factor(
        ncrf1_admission.inpatient_admission_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   NA
                   ),
        ordered = TRUE
        )
    ) %>%

  # Mutate clinical frailty to ordered factor
  mutate(
    ncrf1_comorbid.clinical_frailty_scale = 
      factor(
        ncrf1_comorbid.clinical_frailty_scale,
        levels = c(
          "Fit",
          "Very mild or mild frailty",
          "Moderate or severe frailty",
          NA
          ),
        ordered = TRUE
        )
    ) %>%
  
  # Mutate covid severity to ordered factor
  mutate(
    ncrf1_vital.admission_severity_worst_covid19 = 
      factor(
        ncrf1_vital.admission_severity_worst_covid19,
        levels = c(
          "Uninfected",
          "Ambulatory mild disease",
          "Hospitalised: moderate disease",
          "Hospitalised: severe disease",
          NA
          ),
        ordered = TRUE
        )
    ) %>%
  
  # Mutate ethnicity to ordered factor
  mutate(
    dem.simplified_ethnicity = 
      factor(
        dem.simplified_ethnicity,
        levels = c(
          "White",
          "Black",
          "Asian",
          "Mixed",
          "Other",
          NA
          ),
        ordered = TRUE
        )
    ) %>%

  # Convert NAs to explicit factor to show in table per category
  mutate(
    across(
      where(is.factor),
      ~factor(.)
    )
  ) %>%
  mutate(
    across(
      where(is.factor),
      ~forcats::fct_explicit_na(.)
    )
  )
```

Create list of labels
```{r Create label list}
dat_label_list <- list(
      # demographics
      dem.dob_age ~ "Age",
      dem.sex_at_birth ~ "Sex",
      dem.highest_education ~ "Education",
      dem.is_english_your_first_language ~ "English as First Language",
      dem.simplified_ethnicity ~ "Ethnicity",
      impact.current_employment_status ~ "Employment Status",
      # ncrf data
      ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
      ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
      ncrf1_admission.inpatient_admission_windowed ~ "Date of Inpatient Admission"
      )
```


## Summary Tables

Summary table by case control vaccine
```{r Summary table case control vaccine}
covidcns_sumtable <- table_subset %>%
  
  # Create summary table
  tbl_summary(
    
    # split by case_control_vaccine
    by = case_control_vaccine,
    
    # 2 line summary and show yes/no
    type = list(
      all_continuous() ~ "continuous2",
      all_dichotomous() ~ "categorical"
    ),
    
    # exclude standard missing values
    missing = "no",
    
    # add mean, sd, missing n and missing % for cont vars
    statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
    
    # add custom labels
    label = dat_label_list
              ) %>%
  
  # add labels for missing n/%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  
  # bold variable names
  bold_labels()

# Save table as docx
flextable::save_as_docx(
  as_flex_table(covidcns_sumtable),
  path = "/Users/zainahmad/Library/CloudStorage/OneDrive-SharedLibraries-King'sCollegeLondon/TNG-Public - ilovecovidcns - ilovecovidcns/data_sharing/naomi/steering_group_table.docx"
  )

# View table
covidcns_sumtable
```


# Plots


Create subset for plotting
```{r Subset for plot}
plot_subset <- dat %>%
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   str_detect(case_control_vaccine, "ontrol") ~ "Control",
                                   str_detect(case_control_vaccine, "ase") ~ "Case",
                                   TRUE ~ .)
                )
          )

plot_subset <- subset(plot_subset, !is.na(dem.simplified_ethnicity) &
                  !is.na(case_control_vaccine))

plot_subset_case <- subset(plot_subset, case_control_vaccine == "Case") %>% 
    count(dem.simplified_ethnicity = factor(dem.simplified_ethnicity)) %>% 
    mutate(pct = prop.table(n))

plot_subset_control <- subset(plot_subset, case_control_vaccine == "Control") %>% 
    count(dem.simplified_ethnicity = factor(dem.simplified_ethnicity)) %>% 
    mutate(pct = prop.table(n))

plot_subset %>% count(case_control_vaccine)
```


# Ethnicity Plot


Bar plot ethnicity for cases
```{r Ethnicity case}
pl1 <- ggplot(
  data = plot_subset_case, # pick only cases
  aes(x = dem.simplified_ethnicity,
      y = pct,
      fill = dem.simplified_ethnicity,
      label = scales::percent(pct))
  )


pl1 <- pl1 + geom_col(position = 'dodge')

pl1 <- pl1 + scale_y_continuous(labels=scales::percent_format())

pl1 <- pl1 + xlab("Ethnicity")

pl1 <- pl1 + ylab("Relative Frequency")

pl1 <- pl1 + labs(fill = "Ethnicity")

pl1 <- pl1 + scale_fill_brewer(palette = "Accent")

pl1 <- pl1 + geom_text(position = position_dodge(width = .9),    # move to center of bars
              vjust = -0.5,    # nudge above top of bar
              size = 3)

pl1 <- pl1 + geom_text(x=0.7, y=0.5, label="n=304")

pl1 <- pl1 + theme_bw()

pl1 <- pl1 + 
  ggtitle("Ethnicity for Cases in the COVID-CNS Study") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl1

ggsave(filename = "/Users/zainahmad/Library/CloudStorage/OneDrive-SharedLibraries-King'sCollegeLondon/TNG-Public - ilovecovidcns - ilovecovidcns/data_sharing/naomi/ethnicity_cases_plot_without_missing.png")
```



Bar plot ethnicity for controls
```{r Ethnicity control}
pl1 <- ggplot(
  data = plot_subset_control, # pick only controls
  aes(x = dem.simplified_ethnicity,
      y = pct,
      fill = dem.simplified_ethnicity,
      label = scales::percent(pct))
  )


pl1 <- pl1 + geom_col(position = 'dodge')

pl1 <- pl1 + scale_y_continuous(labels=scales::percent_format())

pl1 <- pl1 + xlab("Ethnicity")

pl1 <- pl1 + ylab("Relative Frequency")

pl1 <- pl1 + labs(fill = "Ethnicity")

pl1 <- pl1 + scale_fill_brewer(palette = "Accent")

pl1 <- pl1 + geom_text(position = position_dodge(width = .9), # move to center of bars
              vjust = -0.5,    # nudge above top of bar
              size = 3)

pl1 <- pl1 + geom_text(x=0.7, y=0.5, label="n=171")

pl1 <- pl1 + theme_bw()

pl1 <- pl1 + 
  ggtitle("Ethnicity for Controls in the COVID-CNS Study") + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(size = 9,
                                   angle = 30,
                                   hjust = 1))

pl1

ggsave(filename = "/Users/zainahmad/Library/CloudStorage/OneDrive-SharedLibraries-King'sCollegeLondon/TNG-Public - ilovecovidcns - ilovecovidcns/data_sharing/naomi/ethnicity_controls_plot_without_missing.png")
```