---
title: "COVIDCNS Cognitive Analysis Summary Tables"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

Create subset of data to table
```{r Subset for table}
table_subset <- dat %>%
  select(
    # sample level grouping
    case_control_vaccine,
    diagnostic_group,
    # demographics
    dem.dob_age,
    dem.sex_at_birth,
    dem.highest_education,
    dem.is_english_your_first_language,
    # demographics memory questions
    dem.concerned_memory,
    dem.concerned_memory_before_covid,
    dem.concerned_memory_after_covid,
    dem.memory_problem_worse_year,
    dem.has_your_memory_got_progressively_worse,
    # mh questionnaires
    gad7.sum_score,
    gad7.binary_clinical,
    phq9.sum_score,
    phq9.binary_depression,
    pcl5.sum_score,
    pcl5.binary_PTSD,
    cfs.sum_score,
    cfs.mental_subscale,
    cfs.physical_subscale,
    # ncrf data
    ncrf1_vital.admission_severity_worst_covid19,
    ncrf1_pre_med.had_covid19_vaccine,
    ncrf1_comorbid.clinical_frailty_scale,
    ncrf1_admission.inpatient_admission_windowed,
    ncrf1_admission.covid_test_windowed,
    ncrf1_lab.crp,
    ncrf1_lab.crp_level,
    ncrf1_lab.wbc_count,
    ncrf1_lab.wbc_count_level,
    ncrf2_lab.crp,
    ncrf2_lab.crp_level,
    ncrf2_lab.wbc_count,
    ncrf2_lab.wbc_count_level,
    ncrf2_med.corticosteroid,
    # cognitron composites
    Composite_global,
    Composite_acc,
    Composite_rt
  ) %>%
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Convert NAs to explicit factor to show in table per category
  mutate(
    across(
      where(is.factor),
      ~factor(.)
    )
  ) %>%
  mutate(
    across(
      where(is.factor),
      ~forcats::fct_explicit_na(.)
    )
  ) %>%
  
  # Mutate windowed admission to ordered factor
  mutate(
    ncrf1_admission.inpatient_admission_windowed = 
      factor(
        ncrf1_admission.inpatient_admission_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   "Other",
                   "Missing"),
        ordered = TRUE
        )
    ) %>%
  
  # Mutate windowed covid test date to ordered factor
  mutate(
    ncrf1_admission.covid_test_windowed = 
      factor(
        ncrf1_admission.covid_test_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   "Other",
                   "Missing"),
        ordered = TRUE
        )
    ) %>%
  # Mutate clinical frailty to ordered factor
  mutate(
    ncrf1_comorbid.clinical_frailty_scale = 
      factor(
        ncrf1_comorbid.clinical_frailty_scale,
        levels = c(
          "Fit",
          "Very mild or mild frailty",
          "Moderate or severe frailty",
          "Missing"
          ),
        ordered = TRUE
        )
    ) %>%
  
  # Mutate covid severity to ordered factor
  mutate(
    ncrf1_vital.admission_severity_worst_covid19 = 
      factor(
        ncrf1_vital.admission_severity_worst_covid19,
        levels = c(
          "Uninfected",
          "Ambulatory mild disease",
          "Hospitalised: moderate disease",
          "Hospitalised: severe disease",
          "Missing"
          ),
        ordered = TRUE
        )
    )
```

Create list of labels
```{r Create label list}
dat_label_list <- list(
      # demographics
      dem.dob_age ~ "Age",
      dem.sex_at_birth ~ "Sex",
      dem.highest_education ~ "Education",
      dem.is_english_your_first_language ~ "English as First Language",
      # demographics memory questions
      dem.concerned_memory ~ "Concerned about Memory",
      dem.concerned_memory_before_covid ~ "Concerned about Memory before COVID",
      dem.concerned_memory_after_covid ~ "Concerned about Memory after COVID",
      dem.memory_problem_worse_year ~ "Memory problem worsened in last year",
      dem.has_your_memory_got_progressively_worse ~ "Memory problem progressively worsening",
      # mh questionnaires
      gad7.sum_score ~ "GAD7 Sumscore (Cutoff = 10)",
      gad7.binary_clinical ~ "GAD7 Algorithmic Diagnosis",
      phq9.sum_score ~ "PHQ9 Sumscore (Cutoff = 10)",
      phq9.binary_depression ~ "PHQ9 Algorithmic Diagnosis",
      pcl5.sum_score ~ "PCL5 Sumscore (Cutoff = 32)",
      pcl5.binary_PTSD ~ "PCL5 Algorithmic Diagnosis",
      cfs.sum_score ~ "Chalder Fatigue Sumscore",
      cfs.mental_subscale ~ "Mental Fatigue",
      cfs.physical_subscale ~ "Physical Fatigue",
      # ncrf data
      ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
      ncrf1_pre_med.had_covid19_vaccine ~ "Had COVID19 Vaccine?",
      ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
      ncrf1_admission.inpatient_admission_windowed ~ "Date of Inpatient Admission",
      ncrf1_admission.covid_test_windowed ~ "Date of Positive COVID19 Test",
      ncrf1_lab.crp ~ "CRP (Module 1)",
      ncrf1_lab.crp_level ~ "CRP Level (Module 1)",
      ncrf1_lab.wbc_count ~ "White Cell Count (Module 1)",
      ncrf1_lab.wbc_count_level ~ "White Cell Count Level (Module 1)",
      ncrf2_lab.crp ~ "CRP (Module 2)",
      ncrf2_lab.crp_level ~ "CRP Level (Module 2)",
      ncrf2_lab.wbc_count ~ "White Cell Count (Module 2)",
      ncrf2_lab.wbc_count_level ~ "White Cell Count Level (Module 2)",
      ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
      # cognitron composites
      Composite_global ~ "Cognitron Global Score",
      Composite_acc ~ "Cognitron Accuracy Score",
      Composite_rt ~ "Cognitron RT Score"
      )
```


## Summary Tables

Summary table by case control vaccine
```{r Summary table case control vaccine}
covidcns_sumtable <- table_subset %>%
  
  # Create summary table
  tbl_summary(
    
    # split by case_control_vaccine
    by = case_control_vaccine,
              
    # exclude diagnostic group
    include = c(
      -diagnostic_group
      ),
    
    # 2 line summary and show yes/no
    type = list(
      all_continuous() ~ "continuous2",
      all_dichotomous() ~ "categorical"
    ),
    
    # exclude standard missing values
    missing = "no",
    
    # add mean, sd, missing n and missing % for cont vars
    statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
    
    # add custom labels
    label = dat_label_list
              ) %>%
  
  # add labels for missing n/%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  
  # bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_sumtable), file = paste0(ilovecovidcns, "/tables/summary/covidcns_sumtable.png"))

# View table
covidcns_sumtable
```

Summary table by diagnostic group
```{r Summary table diagnostic group}
covidcns_sumtable_bycase <- table_subset %>%
  
  tbl_summary(by = diagnostic_group, # same as above except this line
              include = c(-case_control_vaccine),
              type = all_continuous() ~ "continuous2",
              missing = "no",
              statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
              label = dat_label_list
              ) %>%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  bold_labels()

# Save table
gt::gtsave(as_gt(covidcns_sumtable_bycase), file = paste0(ilovecovidcns, "/tables/summary/covidcns_sumtable_bycase.png"))

# View table
covidcns_sumtable_bycase
```
