---
title: "COVIDCNS Cognitive Analysis Summary Tables"
author: "Zain Ahmad"
date: '2022-07-05'
output: html_document
---

Configure global options for all chunks
```{r Setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = '',
  prompt = FALSE,
  cache = FALSE
  )
```

Clear global environment prior to initiation
```{r Clear global environment}
remove(list = ls())
```

Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = "functions/package_check.R")
```

Use package_check to install and load dependencies
Load tidyverse last
```{r Install load dependencies}
packages <- c("sjlabelled",
              "gtsummary",
              "tidyverse")

package_check(packages)
```

Read in file with path to ilovecovidcns channel on Teams
Ensure that your credentials directory is correctly located
```{r Source filepath to ilovecovidcns OneDrive}
source(file = "credentials/paths.R")
```

# Read in clean data

COVIDCNS data
```{r COVIDCNS load data}
dat <- read_rds(
  file = paste0(ilovecovidcns, "/data/covidcns_cognitive_data.rds")
  )

# Inspect dimensions of dataframe 
dat %>%
  dim()
```

## Summary Tables

Summary table by case control vaccine
```{r Summary table case control vaccine}
covidcns_sumtable <- dat %>%
  
  # Mutate vaccine/control to NA, keep case and covid+/- controls
  mutate(across(.cols = case_control_vaccine,
                 .fns = ~case_when(str_detect(case_control_vaccine, "accine") ~ NA_character_,
                                   . == "Control" ~ NA_character_,
                                   TRUE ~ .)
                )
          ) %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Mutate windowed admission to ordered factor
  mutate(
    ncrf1_admission_windowed = 
      factor(
        ncrf1_admission_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   "Other",
                   "Missing"),
        ordered = TRUE
        )
    ) %>%
  
  # Convert NAs to explicit factor to show in table per category
  dplyr::mutate(dem.sex_at_birth = factor(dem.sex_at_birth) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_vital.admission_severity_worst_covid19 = factor(ncrf1_vital.admission_severity_worst_covid19) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf2_med.corticosteroid = factor(ncrf2_med.corticosteroid) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_comorbid.clinical_frailty_scale = factor(ncrf1_comorbid.clinical_frailty_scale) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.concerned_memory = factor(dem.concerned_memory) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.highest_education = factor(dem.highest_education) %>%
                  forcats::fct_explicit_na()) %>%
  
  # Create summary table
  tbl_summary(
    
    # split by case_control_vaccine
    by = case_control_vaccine,
              
    # vars to include
    include = c(dem.dob_age,
                dem.sex_at_birth,
                dem.highest_education,
                ncrf1_vital.admission_severity_worst_covid19,
                ncrf1_comorbid.clinical_frailty_scale,
                ncrf1_admission_windowed,
                gad7.sum_score,
                phq9.sum_score,
                pcl5.sum_score,
                ncrf2_med.corticosteroid,
                dem.concerned_memory,
                Composite_global,
                Composite_acc,
                Composite_rt),
    
    # 2 line summary
    type = all_continuous() ~ "continuous2",
    
    # exclude standard missing values
    missing = "no",
    
    # add mean, sd, missing n and missing % for cont vars
    statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
    
    # add custom labels
    label = list(dem.dob_age ~ "Age",
                 dem.sex_at_birth ~ "Sex",
                 dem.highest_education ~ "Education",
                 ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                 ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                 ncrf1_admission_windowed ~ "Date of Inpatient Admission",
                 gad7.sum_score ~ "GAD7 Sumscore (Cutoff = 10)",
                 phq9.sum_score ~ "PHQ9 Sumscore (Cutoff = 10)",
                 pcl5.sum_score ~ "PCL5 Sumscore (Cutoff = 32)",
                 ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                 dem.concerned_memory ~ "Concerned about Memory",
                 Composite_global ~ "Cognitron Global Score",
                 Composite_acc ~ "Cognitron Accuracy Score",
                 Composite_rt ~ "Cognitron RT Score")
              ) %>%
  
  # add labels for missing n/%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  
  # bold variable names
  bold_labels()

# Save table as png image
gt::gtsave(as_gt(covidcns_sumtable), file = "tables/summary/covidcns_sumtable.png")

# View table
covidcns_sumtable
```

Summary table by diagnostic group
```{r Summary table diagnostic group}
covidcns_sumtable_bycase <- data_joined %>%
  
  # Remove pts missing cognitron
  filter(!is.na(Composite_global)) %>%
  
  # Mutate windowed admission to ordered factor
  mutate(
    ncrf1_admission_windowed = 
      factor(
        ncrf1_admission_windowed,
        levels = c("March 2020 to August 2020",
                   "September 2020 to February 2021",
                   "March 2021 to August 2021",
                   "September 2021 to February 2022",
                   "Other",
                   "Missing"),
        ordered = TRUE
        )
    ) %>%
  
  # Convert NAs to explicit factor to show in table per category
  dplyr::mutate(dem.sex_at_birth = factor(dem.sex_at_birth) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_vital.admission_severity_worst_covid19 = factor(ncrf1_vital.admission_severity_worst_covid19) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf2_med.corticosteroid = factor(ncrf2_med.corticosteroid) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(ncrf1_comorbid.clinical_frailty_scale = factor(ncrf1_comorbid.clinical_frailty_scale) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.concerned_memory = factor(dem.concerned_memory) %>%
                  forcats::fct_explicit_na()) %>%
  
  dplyr::mutate(dem.highest_education = factor(dem.highest_education) %>%
                  forcats::fct_explicit_na()) %>%
  
  # Create summary table with stats to match Kuha's table
  tbl_summary(by = diagnostic_group, # same as above except this line
              include = c(dem.dob_age,
                          dem.sex_at_birth,
                          dem.highest_education,
                          ncrf1_vital.admission_severity_worst_covid19,
                          ncrf1_comorbid.clinical_frailty_scale,
                          ncrf1_admission_windowed,
                          gad7.sum_score,
                          phq9.sum_score,
                          pcl5.sum_score,
                          ncrf2_med.corticosteroid,
                          dem.concerned_memory,
                          Composite_global,
                          Composite_acc,
                          Composite_rt),
              type = all_continuous() ~ "continuous2",
              missing = "no",
              statistic = list(all_continuous() ~ c("{mean} ({sd})", "{N_miss} ({p_miss}%)")),
              label = list(dem.dob_age ~ "Age",
                           dem.sex_at_birth ~ "Sex",
                           dem.highest_education ~ "Education",
                           ncrf1_vital.admission_severity_worst_covid19 ~ "COVID19 Severity",
                           ncrf1_comorbid.clinical_frailty_scale ~ "Clinical Frailty Score",
                           ncrf1_admission_windowed ~ "Date of Inpatient Admission",
                           gad7.sum_score ~ "GAD7 Sumscore (Cutoff = 10)",
                           phq9.sum_score ~ "PHQ9 Sumscore (Cutoff = 10)",
                           pcl5.sum_score ~ "PCL5 Sumscore (Cutoff = 32)",
                           ncrf2_med.corticosteroid ~ "Corticosteroid Administration",
                           dem.concerned_memory ~ "Concerned about Memory",
                           Composite_global ~ "Cognitron Global Score",
                           Composite_acc ~ "Cognitron Accuracy Score",
                           Composite_rt ~ "Cognitron RT Score")
              ) %>%
  modify_table_body(dplyr::mutate,
                    label = ifelse(label == "N missing (% missing)", "Missing", label)
                    ) %>%
  bold_labels()

# Save table
gt::gtsave(as_gt(covidcns_sumtable_bycase), file = "tables/summary/covidcns_sumtable_bycase.png")

# View table
covidcns_sumtable_bycase
```
